% !TEX program = xelatex
% general resume
% by EULIR

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{RUNMING LI}

\basicInfo{
  \email{runmingli\_edu@163.com} \textperiodcentered\ 
  \phone{(+86) 139-8001-6050} \textperiodcentered\ 
  \github[EULIR]{https://github.com/EULIR} \textperiodcentered\ 
  \linkedin[RUNMING LI]{https://www.linkedin.com/in/runming/}
  }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Chengdu Shude Experimental Middle School}, Sichuan, China}{Sep. 2014 -- June. 2017}
GPA (9th grade): 97.00 / 100 unweighted
\datedsubsection{\textbf{Chengdu No.7 High School}, Sichuan, China}{Sep. 2017 -- Present}
Expected Date of Graduation: June. 2020
GPA (10th and 11th grade): 90.23 / 100 unweighted
\datedsubsection{\textbf{SAT}}{Mar. 2019}
Overall: 1480; Reading and Writing: 680; Math: 800; Essay: 6/6/7
\datedsubsection{\textbf{SAT Subject Tests}}{June. 2019}
Math 2: xxx; Physics: xxx
\datedsubsection{\textbf{TOEFL}}{Dec. 2018}
Overall: 111; RLSW: 28/27/29/27
\datedsubsection{\textbf{Advanced Placement (AP)}}{May. 2018, May. 2019}
2018 - Computer Science A: 5; Statistics: 5  \\
2019 - Calculus BC: x; Physics C Electricity and Magnetism: x; Physics C Mechanics: x

\section{\faUsers\ Work Experience}
\datedsubsection{\textbf{Sobey Digital Technology Co., Ltd.}, Sichuan, China}{Mar. 2019 -- Apr. 2019}
\emph{Intern, Assistant Tester}\ \ \ Total hours committed: 200
\begin{itemize}
  \item Tested functionalities of EditMax nonlinear editing system and Vernox database
  \item Prepared the 11.0.6 version release of EditMax and its related work
\end{itemize}


\section{\faCogs\ Academic Activities and Awards}
\datedsubsection{\textbf{Spark Computer Science Club}}{July. 2017 -- Present}
\emph{Club Member}\ \ \ 2 hr/wk for 9 months
\begin{itemize} 
  \item Attended lectures and seminars actively and proposed club improvement plans
  \item Prepared lecture materials for then club leaders and guest lecturers
\end{itemize}
\emph{Acting Club Leader}\ \ \ 2.5 hr/wk for 3 months
\begin{itemize}
  \item Hosted computer science lectures about algorithms, data structure, object-oriented programming, etc
  \item Organized and led an AP CSA study group to prepare for the exam
\end{itemize}
\emph{Club Leader}\ \ \ 3.5 hr/wk
\begin{itemize}
  \item Hosted advanced computer science lectures about game engines, website design, data analysis, etc
  \item Led club members to do hand-on projects such as underwater robots using Arduino (in collaboration with local company XMaker)
\end{itemize}

\datedsubsection{\textbf{Open Source Contributions} on GitHub and Other Platforms}{Jan. 2018 -- Present}
\emph{Open Source Contributor}\ \ \ 2 hr/day
\begin{itemize}
  \item Owned 20+ personal open-sourced projects (including Android apps, website source code, third party plugin for editors and other softwares, binary libraries, etc) with 1000+ contributions
  \item Contributed to 20+ open-sourced repositories with Issues and Pull Requests
\end{itemize}

\datedsubsection{\textbf{Codewars} - Online Coding Challenges Platform}{Jan. 2018 -- Present}
\emph{Solver, Participant}\ \ \ 0.5 hr/day
\begin{itemize}
  \item Solved and contributed Kata actively (one of the major contributors of the community)
  \item Ranked \#287 out of 200,000+ developers worldwide
\end{itemize}

\datedsubsection{\textbf{Project Euler} - Platform to Solve Math Problems Using Computer}{Jan. 2018 -- Present}
\emph{Solver, Participant}\ \ \ 0.5 hr/day
\begin{itemize}
  \item Solved Project Euler mathematics problems daily using Java programming language
  \item Ranked \#79 nationwide (top 0.143\% out of 900,000+ users worldwide)
\end{itemize}

\datedsubsection{\textbf{Carnegie Mellon University Pre-College AP/EA Program}}{June. 2019 -- Aug. 2019}
\emph{Student}
\begin{itemize}
  \item Expected courses: 15-122 Principles of Imperative Computation and 21-127 Concepts of Mathematics
\end{itemize}

\datedsubsection{\textbf{Second Prize in National Olympiad in Informatics in Provinces (NOIP)}}{Dec. 2016}

\section{\faHeartO\ Artistic Activities and Awards}
\datedsubsection{\textbf{Broadcasting Station of Chengdu Shude Experimental Middle School}}{Sep. 2016 -- June. 2017}
\emph{Head of the Broadcasting Station}\ \ \ 0.5 hr/day
\begin{itemize}
  \item Led a team of broadcasters of 10 to provide everyday noon news to all students and faculties 
  \item Tutored lowerclassmen about how to perform recitation on stage and how to be host of important events
  \item Hosted 10+ school events and performed recitation 5+ times (9th grade exclusively)
\end{itemize}

\datedsubsection{\textbf{Host and Recitation Performer in Chengdu No.7 High School}}{Sep. 2017 -- Present}
\emph{Host, Recitation Performer}
\begin{itemize}
  \item Hosted 3+ large-scale school events including Chengdu No.7 High School Educational Webinars, School Opening Ceremony, etc
  \item Composed and Performed 5+ recitation performances both in school and on behalf of school
  \item Led a team of 12 to perform recitation in the Traditional Chinese Recitation Contest held by Chengdu No.7 High School
\end{itemize}

\datedsubsection{\textbf{National First Prize on The 4th National High School Recitation Conference}}{Nov. 2017}
\emph{Main Performer, Composer}
\begin{itemize}
  \item Performed the originally composed Chinese recitation with 3 other performers with the topic of traditional culture of Sichuan and won the national first prize
\end{itemize}

\section{\faBlackTie\ Miscellaneous Extracurricular Activities}
\datedsubsection{\textbf{NeoFuture} - Online Video Channel Facing K-12 Computer Science Education}{Nov. 2018 -- Present}
\emph{Co-founder, Main Contributor}\ \ \ 5 hr/wk
\begin{itemize}
  \item Founded the NeoFuture online video education platform to bring theoretical computer science knowledge to audience that previously cannot have access to CS knowledge
  \item Lectured video episodes with topics in Computer Science history, Artificial Intelligence, etc
  \item Gained 30k+ views on Tencent Video channel and 200+ daily active users
  \iten Developed the official website of NeoFuture and Wechat Mini-Program to provide better video viewing user experience
\end{itemize}

\datedsubsection{\textbf{Public Forum Debate Tournaments}}{Mar. 2018 -- Aug. 2018}
\emph{Debater}
\begin{itemize}
  \item Attended National High School Debate League of China (NHSDLC) regional and national debate tournaments and brought team to Quarterfinal and Octofinal
  \item Won personal 2nd speak award and 8th speak award respectively in two tournaments
\end{itemize}

\datedsubsection{\textbf{2018 MIT Solve}}{May. 2018 -- June. 2018}
\emph{Participant, Main Contributor of the team}\ \ \ 5 hr/wk for 2 months
\begin{itemize}
  \item Developed a wetland park solution in Jinzhou, China to solve salinization of soil in coastal cities
  \item Delivered a pitch speech to introduce to public how wetland parks may work
  \item Won the first prize in MIT Solve Athon with 3 other team members
\end{itemize}

\datedsubsection{\textbf{Great Internet Mersenne Prime Search}}{Jan. 2019 -- Present}
\emph{Volunteer}
\begin{itemize}
  \item Volunteered to work on Great Internet Mersenne Prime Search to find mersenne prime numbers
  \item Proved and verified M88499863 and nine other numbers in Mersenne prime form for being non-prime numbers
\end{itemize}

\datedsubsection{\textbf{First prize winner on the 7th Chengdu Picture Yourself in Perth Contest}}{Feb. 2018}
\emph{Contester, Ambassador}
\begin{itemize}
  \item Represented the Foreign affairs office of the goverment of Chengdu to visit Perth, Australia, sister city of Chengdu, on academic and edcational purposes
  \item Exchanged ideology of edcation systems with the mayor of Perth and the dean of The University of Western Australia, and proposed methods that Perth and Chengdu can collaborate educationally in the future
\end{itemize}

\end{document}
