% !TEX program = xelatex
% general resume
% by EULIR

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{RUNMING LI}

\basicInfo{
  \email{andy@runming.xyz} \textperiodcentered\ 
  \phone{(+86) 139-8001-6050} \textperiodcentered\ 
  \github[EULIR]{https://github.com/EULIR} \textperiodcentered\ 
  \linkedin[RUNMING LI]{https://www.linkedin.com/in/runming/}
  }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Chengdu No.7 High School}, Sichuan, China}{Sep. 2017 -- Jun. 2020}
GPA (10th and 11th grade): 90.23 / 100 unweighted
\datedsubsection{\textbf{Chengdu Shude Experimental Middle School}, Sichuan, China}{Sep. 2014 -- Jun. 2017}
GPA (9th grade): 97.00 / 100 unweighted

\section{\faStar\ Standardized Test Scores}
\begin{itemize}
  \item \textbf{SAT}: Overall: 1480; Reading and Writing: 680; Math: 800; Essay: 6/6/7
  \item \textbf{SAT Subject Tests}: Math 2: xxx; Physics: xxx
  \item \textbf{TOEFL}: Overall: 111; RLSW: 28/27/29/27
  \item \textbf{Advanced Placement (AP)}: \\ 2018 - Computer Science A: 5; Statistics: 5  \\
2019 - Calculus BC: x; Physics C Electricity and Magnetism: x; Physics C Mechanics: x
\end{itemize}

\section{\faUsers\ Work Experience}
\datedsubsection{\textbf{Sobey Digital Technology Co., Ltd.}, Sichuan, China}{Mar. 2019 -- Apr. 2019}
\emph{Intern, Assistant Tester}\ \ \ Total hours committed: 200
\begin{itemize}
  \item Tested functionalities of EditMax nonlinear editing system, a world-class video editing system in Ultra High Definition (UHD) editing (our clients including China Central Television), and Vernox database, a newly designed distributed database specifically for Chinese application scenarios
  \item Evaluated and added test cases for EditMax and Vernox to ensure they work under different unexpected circumstances \item Discovered, reported, and fixed 20+ bugs of EditMax system and Vernox database 
\end{itemize}


\section{\faCogs\ Science and Technology Activities and Awards}
\datedsubsection{\textbf{Spark Computer Science Club}}{Jul. 2017 -- Present}
\emph{Club Member}\ \ \ 2 hrs/wk in grade 10
\begin{itemize} 
  \item Attended lectures and seminars actively and proposed club improvement plans
  \item Prepared lecture materials for then club leaders and guest lecturers
\end{itemize}
\emph{Club President}\ \ \ 4 hrs/wk in grade 11 - 12
\begin{itemize}
  \item Hosted computer science lectures about algorithms, data structure, object-oriented programming, etc
  \item Hosted advanced computer science lectures about game engines, website design, data analysis, etc
  \item Organized and led an AP CSA study group to prepare for the exam
  \item Led club members to do hand-on projects such as underwater robots using Arduino (in collaboration with local company XMaker)
\end{itemize}

\datedsubsection{\textbf{NeoFuture} - Online Video Channel Facing K-12 Computer Science Education}{Nov. 2018 -- Present}
\emph{Co-founder, President}\ \ \ 5 hrs/wk, 25 wks/yr
\begin{itemize}
  \item Founded the NeoFuture online video education platform to bring theoretical computer science knowledge to audience that previously cannot have access to CS knowledge
  \item Lectured video episodes with topics in Computer Science history, Artificial Intelligence, etc
  \item Gained 30k+ views on Tencent Video channel and 200+ daily active users
  \item Developed the official website and Wechat Mini-Program  of NeoFuture to provide better video viewing user experience
\end{itemize}

\datedsubsection{\textbf{Open Source Contributions} on GitHub, the Community of Developers to Build and Share Open Source Projects \qquad }{Jan. 2018 -- Present}
\emph{Open Source Contributor}\ \ \ 2 hrs/d
\begin{itemize}
  \item Owned 20+ personal open-source projects (including Android apps, website source code, third party plugin for editors and other software, binary libraries, etc) with 1000+ contributions (commits) and 10+ programming languages
  \item Contributed to 20+ open-source repositories with Issues (bug report) and Pull Requests (bug fix)
\end{itemize}

\datedsubsection{\textbf{Carnegie Mellon University Pre-College AP/EA Program}}{Jun. 2019 -- Aug. 2019}
\emph{Student}
\begin{itemize}
  \item Expected courses: 15-122 Principles of Imperative Computation and 21-127 Concepts of Mathematics
\end{itemize}

\datedsubsection{\textbf{Codewars} - Online Coding Challenges Platform}{Jan. 2018 -- Present}
\emph{Solver, Participant}\ \ \ 0.5 hr/d
\begin{itemize}
  \item Solved and contributed Kata actively (one of the major contributors of the community)
  \item Ranked \#252 out of 200,000+ developers worldwide
\end{itemize}

\datedsubsection{\textbf{Project Euler} - Platform Dedicated to Solve Mathematical Problems with Computer Skills}{Jan. 2018 -- Present}
\emph{Solver, Participant}\ \ \ 0.5 hr/d
\begin{itemize}
  \item Solved Project Euler mathematics problems daily using Java programming language
  \item Ranked \#76 nationwide (top 0.143\% out of 900,000+ users worldwide)
\end{itemize}

\datedsubsection{\textbf{Great Internet Mersenne Prime Search (GIMPS)} - a Collaborative Project of Volunteers to Search for Mersenne Prime Numbers}{Jan. 2019 -- Present}
\emph{Volunteer}
\begin{itemize}
  \item Volunteered to work on \emph{Great Internet Mersenne Prime Search} to find Mersenne prime numbers
  \item Proved and verified M88499863 and nine other numbers in Mersenne prime form for being non-prime numbers
\end{itemize}

\datedsubsection{\textbf{2018 MIT Solve}}{May 2018 -- Jun. 2018}
\emph{Participant, Main Contributor of the team}\ \ \ 5 hrs/wk for 2 months
\begin{itemize}
  \item Developed a wetland park solution in Jinzhou, China to solve salinization of soil in coastal cities
  \item Delivered pitch speeches to introduce to public about the details of our wetland park solution
  \item Won the first prize in MIT Solveathon with 3 other team members
\end{itemize}

\datedsubsection{\textbf{Second Prize in National Olympiad in Informatics in Provinces (NOIP)}}{Dec. 2016}

\section{\faHeartO\ Debate and Performing Arts Activities and Awards}
\datedsubsection{\textbf{Broadcasting Station of Chengdu Shude Experimental Middle School}}{Sep. 2016 -- Jun. 2017}
\emph{Head of the Broadcasting Station}\ \ \ 0.5 hr/d
\begin{itemize}
  \item Led a team of 10+ broadcasters to provide everyday noon news to all students and faculties on campus
  \item Tutored lowerclassmen about how to perform recitation on stage and how to be host of important events
  \item Hosted 10+ school events and performed recitation 5+ times (9th grade exclusively)
\end{itemize}

\datedsubsection{\textbf{Host and Recitation Performer in Chengdu No.7 High School}}{Sep. 2017 -- Present}
\emph{Host, Recitation Performer}
\begin{itemize}
  \item Hosted 3+ large-scale school events including Chengdu No.7 High School Educational Seminars, School Opening Ceremony, etc
  \item Composed and performed 5+ recitation performances either in school or on behalf of school
  \item Led a team of 12 to perform recitation in the Traditional Chinese Recitation Performance Show held by Chengdu No.7 High School
\end{itemize}

\datedsubsection{\textbf{National First Prize in The 4th National High School Recitation Conference}}{Nov. 2017}
\emph{Main Performer, Composer}
\begin{itemize}
  \item Performed the originally composed Chinese recitation with 3 other performers with the topic of traditional culture of Sichuan and won the national first prize
\end{itemize}

\datedsubsection{\textbf{Public Forum Debate Tournaments}}{Mar. 2018 -- Aug. 2018}
\emph{Debater}
\begin{itemize}
  \item Attended National High School Debate League of China (NHSDLC) regional and national debate tournaments and brought team to Quarterfinal and Octofinal
  \item Won personal 2nd speaker award and 8th speak award respectively in two tournaments
\end{itemize}

\datedsubsection{\textbf{First Prize Winner on The 7th Chengdu Picture Yourself in Perth Contest}}{Feb. 2018}
\emph{Contestant, Ambassador}
\begin{itemize}
  \item Represented the Foreign affairs office of the government of Chengdu to visit Perth, Australia, sister city of Chengdu, on academic and educational purposes
  \item Exchanged ideology of education systems with the mayor of Perth and the dean of The University of Western Australia, and proposed methods that Perth and Chengdu can collaborate educationally in the future
\end{itemize}

\end{document}
